Clustering time series based on probability distributions across temporal granularities

### 2021-11-11 main.Rmd
group summary updated only with wnwd
added sindex plot for wpd approach

```{r opt-cluster-tsne-jsd, fig.cap = "(a) shows t-SNE summary of the $24$ selected customers chosen through prototype selection, (b) shows a plot of sindex for different cluster size for clustering based on JS-based distances. The separation index decreases sharply from $5$ to $6$ clusters, so $5$ clusters are used here."}

@@

```{r data-heatmap-hod-group}
```

```{r data-heatmap-moy-group}

>>>>

```{r opt-cluster-tsne-jsd-png, fig.cap = "(a) shows t-SNE summary of the $24$ selected customers chosen through prototype selection, (b) and (c) shows a plot of sindex for different cluster size for clustering based on JS-based distances and wpd-distances respectively. The plot suggests optimal number of clusters as $4$ and $7$ respectively."}
include_graphics("figs/opt_clust_parenthesis.png")
```

@@

```{r data-heatmap-hod-group-new}
```

```{r data-heatmap-moy-group-new}
